Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-05-25 dis_clusion.tex
add ref +add SQ mention

The tail recycling allows for each model a huge gain in productivity, even for
then model B for which it does not change the number of levels required to reach
$90w\%$ of $^{235}$U in the uranium. Even if no cascades chaining also to
retrieve the same production rate as a direct enrichment, the model B with
reprocessing reach about $80\%$ of an optimum production, which is far from
being negligible\ldots

>>>>

The tail recycling allows for each model a huge gain in productivity, even for
then model B for which it does not change the number of levels required to reach
$90w\%$ of $^{235}$U in the uranium. Even if no cascades chaining also to
retrieve the same production rate as a direct enrichment, the model B with
reprocessing reach about $80\%$ of an optimum production, which is far from
being negligible, allowing to build up a Significant Quantity of \gls{HEU} in
less than 8 months\ldots
